---
title: "W_UP_01"
author: "Th3b0yn3xtd00r"
date: "Summer 2023"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

We are trying to find the average number of push ups between skill players and line players. Is there a statistical difference in the average number of push ups between both positions?

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of push ups of line vs skill players

$H_A$: The average number of push ups done by line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

The response variable we are using is Numerical~Categorical. The number of push-ups is numerical while the categorical is the different positions (Line players and Skill players). Other methods we will be using is the box plot and we are utilizing the numerical summary and numerical descriptive results and t-test.

# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
boxplot(pushups~position,data=mydata)
```

The box plot show that the skill players on average do about sixty push ups while the line players are able to do less than twenty push ups in about two minutes.
The positions have a significant difference.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(pushups~position,data=mydata)
```

Based off the numerical results between Line and Skill players shows a significant difference with thirty-three push ups being range. The mean for the Line players is seventeen push ups while the Skill players are able to do fifty push ups within two minutes.

## Inferential Results

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(pushups~position,data=mydata)
```

According to T-test it shows that there is a difference between the average amount of push ups is thirty-three push ups from the Line players and the Skill players since the p- value which is 00000.9421 is too small which also caused us to reject the null hypothesis. The 95 percent of the time the skill players do between 20 and 45 more push ups in two minutes than a line player.

# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

The original question was who was able to do more push ups on average within two minutes, the line players or the skill players? I came to the conclusion that on average there was a thirty-three push up range between the two. The line players were able to do about seventeen push ups while the Skill players were able to do about fifty push ups on average within two minutes. The 95 percent of the time was differential with it being ranged from twenty to fifty push ups more than a line player. The p-value of 00000.9421 is too small so it forces us to reject the null hypothesis.

